Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-06-11 supplement/05_calibration_data.Rmd
add text explaining get data opts

We get spatial and summary ouput of the residence patch method using the `atl_patch_summary` function using the options `which_data` = "spatial" and `which_data` = "summary.
We use a buffer radius here of 20 metres for the spatial buffer, despite using a buffer radius of 5 metres earlier, simply because it is easier to visualise in the output figure.

>>>>

Having classified slow-moving or stationary behavioural bouts into residence patches, many animal ecologists would most probably wish to know something about the environment at or around these patches --- more accurately, around the point locations classified into patches.

How exactly this is done depends on the relative spatial scales of the residence patches and the resolution of the environmental data layer.
For instance, a residence patch some 40m -- 50m wide or long may be overlaid on an environmental raster layer with a resolution of 250m.
In this case, sampling the layer at the centroid of the patch is as good as sampling at all the patch's points -- the mean is unlikely to differ (except at raster pixel boundaries).

On the other hand, a raster with a 10m resolution (e.g. Sentinel 1 and 2 data) may be worthwhile to sample at all the locations comprising a residence patch, so as to calculate the mean and variance of environmental conditions.

Furthermore, many (if not all) animals integrate cues from quite a distance (10m -- 100m) when making decisions on when to settle in an area, and when to leave. Thus it can also be useful to sample environmental layers not at point locations, but to extract the mean and variance from an _area_, or a buffer, around the animal's point locations.

We have provided a convenient function to get either _(1)_ the points (classified into patches), or _(2)_ a summary ouput of the residence patches (i.e., the median coordinates and their attributes), or finally _(3)_ a spatial buffer around the points from _(1)_. 
This function, `atl_patch_summary` implements these options using the `which_data` argument, where the options are _(1)_ "points", _(2)_ "summary", or _(3)_ "spatial".

Here, we choose option (3), using a spatial buffer of 20m. The distance of the bufffer is passed to the argument `buffer_radius`.
